SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-03-01 scipy-1.0/scipy-optimize.tex
minimized minimize

The \texttt{minimize} function provides methods for finding local minima of
nonlinear optimization problems. It unifies several methods with a common 
interface in order to facilitate interchanging between solvers with different
characteristics. Characteristics of the different methods are summarized in 
Table~\ref{tab:minimize-si}.
%% Currently, this introduces a ton of whitespace around a very simple expression (min f(x)). The reader can easily find the standard of meaning of `nonlinear programming', so I believe it should be removed. If we decide that it is appropriate to include, then we should add the entire problem statement - including constraints - and we should also include the entire linear programming problem statement in the previous section.
% summarizes all the methods available for solving minimization problems of the type:
%\begin{equation}
%  \label{eq:minimization-prob}
%  \min_x f(x)
%\end{equation}
%where $f$ is a multivariate function $f: \mathbb{R}^n \rightarrow \mathbb{R}$ and $x \in \mathbb{R}^n$.
%%  Without the problem statement this sentence isn't really appropriate.
%\texttt{COBYLA} and \texttt{SLSQP} methods support nonlinear constraints, \texttt{L-BFGS-B} and \texttt{TNC} allow box constraints $x^l \le x \le x^u$,
%and the remaining methods are for unconstrained problems.

% The available methods implement a variety of solution strategies.
Derivative-free methods (e.g. \texttt{Nelder-Mead}, \texttt{Powell} and \texttt{COBYLA}) are appropriate for minimizing non-differentiable or
noisy objective functions. When derivatives are available, however, other methods offer faster convergence rates
and have proven convergence properties. 
The derivative-based methods start with an initial guess and refine it iteratively, seeking
a local solution to the optimization problem. Each of these algorithms implements one of two complementary strategies:
line-search or trust-region. At each iteration, the line-search (LS) methods choose a direction
and approximate the optimal point in the given direction. Trust-region (TR) methods, on the other
hand, choose a ``trust-region'' region for which a local model is valid and approximate the best point
inside.

One recently-added trust-region method is \texttt{trust-exact},
which achieves fast convergence by solving the trust-region subproblem almost exactly.
Unfortunately, it requires the Hessian to be stored and factored every iteration, which may preclude
the solution of large problems (e.g.~problems with more than 1000 variables).
Other methods are appropriate for large-scale problems, including
\texttt{CG}, which does not use second derivatives and thus has low memory requirements, and \texttt{L-BFGS-B}, which maintains a simple and compact representation of the Hessian.
\texttt{Newton-CG}, \texttt{trust-ncg} and \texttt{trust-krylov} use second order derivatives to achieve faster
convergence, but are still appropriate for large problems because they factorize the Hessian in an inexact and iterative way that does not require the Hessian to be stored.
The method \texttt{trust-krylov}, introduced in the latest release, is a good compromise between
\texttt{trust-ncg} and \texttt{trust-exact}: it provides a more accurate solution to the trust-region
subproblem than \texttt{trust-ncg}, but it does not require the Hessian to be stored and factored as in \texttt{trust-exact}.

While most \texttt{minimize} development prior to SciPy 1.0 has focused on unconstrained minimization, 
% methods \texttt{SLSQP} and \texttt{COBYLA}\footnote{We note that any equality constraint $c_{\text{eq}}(x) = 0$ can be expressed as two inequality constraints $c_{\text{eq}}(x) \leq 0$ and $-c_{\text{eq}}(x) \leq 0$} 
\texttt{SLSQP} supports fully general nonlinear programming. However, it does not provide special treatment for sparsity, limiting its utility to small problems. Accordingly, ongoing development efforts for \texttt{minimize} are focused on the addition of nonlinear programming algorithms for large, sparse problems.

>>>>

The \texttt{minimize} function unifies several methods of finding local minima of nonlinear optimization problems in a common interface. Four new methods for unconstrained optimization were added to \texttt{minimize} in recent versions of SciPy: \texttt{dogleg}, \texttt{trust-ncg}, \texttt{trust-exact}, and \texttt{trust-krylov}. All are trust-region methods that build a local model of the objective function based on first- and second-derivative information, approximate the best point within a local ``trust region'', and iterate until a local minimum of the original objective function is reached, but each has unique characteristics that make it appropriate for certain types of problems. For instance, \texttt{trust-exact} achieves fast convergence by solving the trust-region subproblem almost exactly, but it requires the second-derivative Hessian matrix to be stored and factored every iteration, which may preclude the solution of large problems ($\geq 1000$ variables). On the other hand, \texttt{trust-ncg} and \texttt{trust-krylov} are well-suited to large-scale optimization problems because they do not need to store and factor the Hessian explicitly, instead using second-derivative information in a faster, approximate way. A detailed comparison of the characteristics of all \texttt{minimize} methods is presented in Table~\ref{tab:minimize-si}.
